RickView: Lightweight Standalone Knowledge Graph Browsing

### 2023-12-18 paper.tex
start use cases

>>>>

\section{Use Cases}
SNIK/ANNO/HITO ?
-> easier docker setup than virtuoso, less resources, Java

LinkedSpending
frequent downtimes
HDT

RuThes
-> LodView instance currently shut down because of memory usage
-> test instance of RickView uses ...
\url{http://ruthes.org/download/ruthes-cloud-corrected-2.ttl.zip}

TODO: check presentation of Leipzig Semantic Web Day for reusable materials
